Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/01_related_work.tex
Squash, conform.
Add maneesh paper.

@@

\noindent{\textbf{Computational Visualization Understanding.}} Pineo \textit{et al.}~\cite{Pineo2012_computational_perception} create a computational model of human vision based on neural networks. Their simulations show that understanding visualization triggers neural activity in high-level areas of cognition, with the authors suspecting that this activity is supported by low-level neurons performing elementary perceptional tasks. Other work tries to parse infographics by finding higher-level saliency models~\cite{bylinskii2016should}, or by extracting text or key visual elements from visualizations~\cite{diagram_understanding,kembhavi2016diagram,zoya_text_visual_tags}. However, these works do not investigate computational understanding of elementary perceptual tasks such as curvature, lengths, or position, which are the building blocks of visualization.

@@

\noindent{\textbf{Visual-cortex-inspired Machine Learning.}} The human visual cortex allows us to recognize objects in the world seemingly without effort (though few remember their infancy). This visual system is organized in layers, which inspired computational classifiers based on multilayer neural networks. Fukushima and Miyake developed the early Neocognitron quantitative model~\cite{fukushima1982neocognitron}, which ultimately led to the work of Hinton, Bengio, and LeCun~\cite{lecun2015deep} and today's GPU-powered \emph{deep} neural networks. Such networks exist with many architectures. For this paper, we compare a set of networks with different architectures and depths, plus networks with weights trained on natural images and on the elementary perceptual reasoning tasks themselves.
%Object detection is extremely difficult and therefore is especially impressive as light intensities can change by levels of magnitude and contrast between foreground and background is so often low. 
%In addition, the visual scene changes every time the human body or human eyes move. 
%This visual system exhibits a very noisy structure but because it is organized by layers it has inspired the mathematical theory of multilayer neural networks.

>>>>

%

@@

\\~\\
\noindent{\textbf{Computational Visualization Understanding.}} Pineo \textit{et al.}~\cite{Pineo2012_computational_perception} create a computational model of human vision based on neural networks. Their simulations show that understanding visualization triggers neural activity in high-level areas of cognition, with the authors suspecting that this activity is supported by low-level neurons performing elementary perceptional tasks. Other work tries to parse infographics by finding higher-level saliency models~\cite{bylinskii2016should}, or by extracting text or key visual elements from visualizations using computer vision techniques~\cite{diagram_understanding,kembhavi2016diagram,zoya_text_visual_tags,maneesh_deconstructing_d3}. However, these works do not investigate computational understanding of elementary perceptual tasks such as curvature, lengths, or position, which are the building blocks of visualization.
%

@@

\\~\\
\noindent{\textbf{Visual-cortex-inspired Machine Learning.}} The human visual cortex allows us to recognize objects in the world seemingly without effort (though few remember their infancy). This visual system is organized in layers, which inspired computational classifiers based on multilayer neural networks. Fukushima and Miyake developed the early Neocognitron quantitative model~\cite{fukushima1982neocognitron}, which ultimately led to the work of Hinton, Bengio, and LeCun~\cite{lecun2015deep} and today's GPU-powered \emph{deep} neural networks. Such networks exist with many architectures. For this paper, we compare a set of networks with different architectures and depths, plus networks with weights trained on natural images and on the elementary perceptual reasoning tasks themselves.
%Object detection is extremely difficult and therefore is especially impressive as light intensities can change by levels of magnitude and contrast between foreground and background is so often low. 
%In addition, the visual scene changes every time the human body or human eyes move. 
%This visual system exhibits a very noisy structure but because it is organized by layers it has inspired the mathematical theory of multilayer neural networks.
